Probabilistic Forecast Reconciliation

### 2018-11-05 Presentation/ProbForeRec.tex
revamp first few motivating slides

\documentclass{beamer}
\usetheme{Warsaw}
\usepackage{amsmath,amsthm, bm, tikz,qtree}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\title{Probabilistic Forecast Reconciliation}
\date{August 15, 2018}
\author[GPAH]{Puwasala Gamakumara, Anastasios Panagiotelis, George Athanasopoulos and Rob Hyndman}
\begin{document}
  \begin{frame}
    \maketitle
  \section{Concepts}

>>>>

\documentclass{beamer}
\usetheme{Warsaw}
\usepackage{amsmath,amsthm, bm, tikz,qtree}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\title{Probabilistic Forecast Reconciliation}
\date{August 15, 2018}
\author[GPAH]{Puwasala Gamakumara, Anastasios Panagiotelis, George Athanasopoulos and Rob Hyndman}
\begin{document}
  \begin{frame}
    \maketitle
  \end{frame}
  \section{Concepts}
  \begin{frame}{Motivating Examples}
  \begin{itemize}
  	\item Gross Domestic Product
  	\begin{itemize}
  		\item An aggregate of consumption, investment, government spending and trade balance
  		\item Further breakdown, e.g. consumption of food, rent, etc.
  	\end{itemize}
    \item Retail sales
    \begin{itemize}
    	\item Aggregate of different product category sales
    	\item Further breakdown into individual stock keeping units.  
    \end{itemize}
    \item Potentially need forecasts of all time series.
  \end{itemize}
  \end{frame}
  \begin{frame}{Incoherent Forecasts}
  \begin{itemize}
    \item Potential approaches
  	\begin{itemize}
  		\item Univariate models
  		\item Multivariate models
  		\item Judgemental forecasts
  	\end{itemize}
  \item Forecasts may not respect aggregation structure. ({\bf Incoherent})
  \item Outcome {\em will} respect aggregation  structure. ({\bf Coherent})
  \item Motivation is aggregation but can be generalised to any linear constraints.
  \end{itemize}
  \end{frame}
  \begin{frame}{Reconciliation}
  \begin{itemize}
  	\item Begin with a vector of forecasts that are incoherent.
  	\item Adjust these {\bf ex post} to make them coherent.
  	\item There are good solutions for point forecasting that:
  	\begin{itemize}
  		\item Guarantee coherent forecasts.
  		\item Improve forecast accuracy overall.
  	\end{itemize}
  	\item Generalisation to probabilistic forecasts is our contribution.
  	\item Getting there necessitates a rethink of the existing point forecasting literature. 
  \end{itemize}
  \end{frame}
